Optimum Control Problem (OCP) consists in determining the vector of control variables to minimize an objective function subject to algebraic-differential constraints. In general, this problem can be solved considering two types of approaches, namely, Direct and Indirect. The first consists in transforming the original problem into an equivalent of nonlinear programming problem. On the other hand, Indirect approach consists in application of optimality conditions to transform the original problem into an equivalent of algebraic-differential boundary value problem. Due to inherent difficulty in solving this boundary value problem, the scientific community has used, preferably, the Direct Methods for solving OCPs. In this context, in specialized literature several numerical packages based on Direct approach for solving OCPs can be found. Despite the wide variety of packages available, there are few studies to evaluate the efficiency and general characteristics. In this contribution, the main aim is to present a comparative study considering some solvers for the resolution of PCOs. For this purpose, the COPILOTS package, that implements the Trapezoidal and Hermite-Simpson Collocation Methods for solving OCP was developed. The results obtained demonstrates that COPILOTS was able to obtain good results in terms of the objective function value, number of objective function evaluations and number of collocation points in comparison with PSOPT and FALCON solvers. Finally, it is important to note that COPILOTS is a package developed for users with little experience in optimal control, easy to implement and use. 

\noindent \textbf{Keywords}: Optimal Control. Direct Methods. Comparative study. Computational Packages.